The development of infants' responses to mispronunciations: A Meta-Analysis

### 2019-05-24 VonHolzenBergmann_MPMetaAnalysis.Rmd
begin updated random effects structure change

@@

@@

rma_correct = rma.mv(g_calc, g_var_calc, data = db_ET_correct, random = ~ same_infant_calc | short_cite)

@@

@@

rma_MPeffect <- rma.mv(g_calc, g_var_calc, mods = ~condition, data = dat, random = ~ same_infant_calc | short_cite)

>>>>

db_ET_correct$short_cite.same_infant_calc <- paste0(db_ET_correct$short_cite, ".", db_ET_correct$same_infant_calc)
db_ET_MP$short_cite.same_infant_calc <- paste0(db_ET_MP$short_cite, ".", db_ET_MP$same_infant_calc)

db_ET_correct$unique_row <- factor(seq(from = 1, to = nrow(db_ET_correct), by = 1))
db_ET_MP$unique_row <- factor(seq(from = 1, to = nrow(db_ET_MP), by = 1))

@@

dat$unique_row <- factor(seq(from = 1, to = nrow(dat), by = 1))

#dat$short_cite.same_infant_calc <- paste0(dat$short_cite, ".", dat$same_infant_calc)
#random = list(~ same_infant_calc | short_cite, ~ unique_row |  short_cite.same_infant_calc)

@@

# rma_correct = rma.mv(g_calc, g_var_calc, data = db_ET_correct, random = ~ same_infant_calc | short_cite)

# new random effects structure
rma_correct = rma.mv(g_calc, g_var_calc, data = db_ET_correct, random = list(~ same_infant_calc | short_cite, ~ unique_row |  short_cite.same_infant_calc))

@@

#rma_MP = rma.mv(g_calc, g_var_calc, data = db_ET_MP, random = ~ same_infant_calc | short_cite)

#
rma_MP = rma.mv(g_calc, g_var_calc, data = db_ET_MP, random = list(~ same_infant_calc | short_cite, ~ unique_row |  short_cite.same_infant_calc))

@@

rma_MPeffect <- rma.mv(g_calc, g_var_calc, mods = ~condition, data = dat, random = list(~ same_infant_calc | short_cite, ~ unique_row |  short_cite.same_infant_calc))
